---
title: "Identify Judicial Empathy: Replication"
date: "February 13, 2019"
author: "Sean Hughes, Keeley MacAfee, Gabe Walker"
output: html_document
---

```{r setup, include=FALSE, echo = FALSE, display = FALSE}

knitr::opts_chunk$set(echo = TRUE)

# Load Required Libraries

library(Zelig)
library("ZeligChoice")
library(xtable)
library(reshape)
library(apsrtable)
library(stargazer)
library(rms)
library(knitr)
library(tidyverse)
library(dplyr)
library(pander)
library(kableExtra)
library(stats)
```

Good idea to include brief abstract at beginning of replications

```{r LOADDATA, echo = FALSE, display = FALSE, include = FALSE}

########################################################
## Loading the Data
########################################################

## This loads three data sets
## 1. Gender cases
## 2. Cleaned by-judge data
## 3. Non-gender cases, downloaded from Kuersten and Haire's website
## (Commented out; their data are available from their website)

# Read in a file that has many court case records
# with associated judge information.
women.cases <- read.csv("./glynn_sen_daughters_by_case_1.csv",
  stringsAsFactors = FALSE
)

# Filter the data for only cases
# with female plaintiffs.
women.cases <- subset(women.cases, femplaintiff == 1)

# Filter the data again for specific cases about
# employment, Title IX, or reproductive issues.
women.cases <- subset(
  women.cases,
  area == "employment" |
    area == "Title IX" |
    area == "pregnancy" |
    area == "abortion" |
    area == "reproductive rights"
)

# Use a factor to alter the order of and
# rename the case topics.
women.cases$area <- factor(women.cases$area,
  levels = c(
    "abortion",
    "employment",
    "pregnancy",
    "reproductive rights",
    "Title IX"
  )
)

## Read in all cases, including non-gender cases
# (from Ashlyn Kuersten/Susan Haire's coding).
# cases <- read.csv("cases.for.analysis.csv")

# Read in only data about
# judges (family, circuit,
# demographics, etc.).
judge.means <- read.csv("glynn_sen_daughters_by_judge.csv",
  stringsAsFactors = FALSE
)

# Ignore all judges without information
# about their children.
all <- subset(judge.means, girls != "NaN")
```

```{r TABLE1, echo = FALSE, display = FALSE, include = FALSE}

########################################################
## Table 1: Number of Children and Girls
########################################################

# Use the table function to create a table of the counts
# of children for all Democrats (0) and Republicans (1).
aa <- table(all$republican, all$child)

# Do the same for counts of girls.
bb <- table(all$republican, all$girls)

# Transform the table into a dataframe
# so it can be manipulated more easily.
dataFramed <- aa %>%
  as.data.frame.matrix()

# Add an additional column for the
# total counts of children and a name
# for the new column.
dataFramedSum <- cbind(dataFramed, rowSums(dataFramed))
colnames(dataFramedSum)[colnames(dataFramedSum) == "rowSums(dataFramed)"] <- "N"

# Create row names for the columns.
row.names(dataFramedSum) <- c("Democrat", "Republican")

# Use the as.data.frame to transform the
# completed table for girls into a data frame.
dataFramedBB <- bb %>%
  as.data.frame.matrix()

# Create a new column (as above) for
# the total number of girls per group,
# and add a title.
dataFramedSumBB <- cbind(dataFramedBB, rowSums(dataFramedBB))
colnames(dataFramedSumBB)[colnames(dataFramedSumBB) ==
  "rowSums(dataFramedBB)"] <- "N"

# Create row names for the columns.
row.names(dataFramedSumBB) <- c("Democrat", "Republican")
```

```{R table1Output, echo = FALSE}

########################################################
## Table 1 (printing)
########################################################

# Use Kable to output the two tables
# that contain the number of children
# per party group.
kable(dataFramedSum, caption = "Table 1: Number of Children and Girls 
      for U.S. Courts of Appeals Judges Participating in Gender-Related
      Cases, 1996-2002") %>%
  kable_styling(full_width = F)

# Use Kable to output the second part
# of the table with just girls.
kable(dataFramedSumBB, caption = "Table 1: Part 2") %>%
  kable_styling(full_width = F)
```

Really nice looking Table 1, also very elegant code used to create it


```{r, echo = FALSE}

########################################################
## Table 2: Judge Demographics
########################################################

# Use the subset function like a filter to
# create new groups that match the given trait,
# in this case Democrats, Republicans, women,
# and men.
dems <- subset(all, republican == 0)
reps <- subset(all, republican == 1)
women <- subset(all, woman == 1)
men <- subset(all, woman == 0)

# Find the mean number of children and
# girls for each of the four groups above.
mean.kids <- cbind(
  mean(na.omit(all$child)),
  mean(na.omit(dems$child)),
  mean(na.omit(reps$child)),
  mean(na.omit(women$child)),
  mean(na.omit(men$child))
)

mean.girls <- cbind(
  mean(na.omit(all$girls)),
  mean(na.omit(dems$girls)),
  mean(na.omit(reps$girls)),
  mean(na.omit(women$girls)),
  mean(na.omit(men$girls))
)

# In the below lines, find the proportion
# of individuals in the four groups above
# who have no children to 6+ children.
prop.zero <- cbind(
  prop.table(table(na.omit(all$child)))[1],
  prop.table(table(na.omit(dems$child)))[1],
  prop.table(table(na.omit(reps$child)))[1],
  prop.table(table(na.omit(women$child)))[1],
  prop.table(table(na.omit(men$child)))[1]
)

prop.one <- cbind(
  prop.table(table(na.omit(all$child)))[2],
  prop.table(table(na.omit(dems$child)))[2],
  prop.table(table(na.omit(reps$child)))[2],
  prop.table(table(na.omit(women$child)))[2],
  prop.table(table(na.omit(men$child)))[2]
)

prop.two <- cbind(
  prop.table(table(na.omit(all$child)))[3],
  prop.table(table(na.omit(dems$child)))[3],
  prop.table(table(na.omit(reps$child)))[3],
  prop.table(table(na.omit(women$child)))[3],
  prop.table(table(na.omit(men$child)))[3]
)

prop.three <- cbind(
  prop.table(table(na.omit(all$child)))[4],
  prop.table(table(na.omit(dems$child)))[4],
  prop.table(table(na.omit(reps$child)))[4],
  prop.table(table(na.omit(women$child)))[4],
  prop.table(table(na.omit(men$child)))[4]
)

prop.four <- cbind(
  prop.table(table(na.omit(all$child)))[5],
  prop.table(table(na.omit(dems$child)))[5],
  prop.table(table(na.omit(reps$child)))[5],
  prop.table(table(na.omit(women$child)))[5],
  prop.table(table(na.omit(men$child)))[5]
)

prop.five <- cbind(
  prop.table(table(na.omit(all$child)))[6],
  prop.table(table(na.omit(dems$child)))[6],
  prop.table(table(na.omit(reps$child)))[6],
  prop.table(table(na.omit(women$child)))[6],
  prop.table(table(na.omit(men$child)))[6]
)

aa <- table(na.omit(all$child))
plus6.all <- sum(aa[7:length(aa)]) / sum(aa)

bb <- table(na.omit(dems$child))
plus6.dems <- sum(bb[7:length(bb)]) / sum(bb)

cc <- table(na.omit(reps$child))
plus6.reps <- sum(cc[7:length(cc)]) / sum(cc)

dd <- table(na.omit(women$child))
plus6.women <- sum(dd[7:length(dd)]) / sum(dd)

ee <- table(na.omit(men$child))
plus6.men <- sum(ee[7:length(ee)]) / sum(ee)

prop.six.or.greater <- cbind(
  plus6.all, plus6.dems,
  plus6.reps, plus6.women, plus6.men
)

# Find similar demographic information,
# specifically proportion female,
# Republican, white, year born (fractional),
# and number of judges in each
# of the four groups defined above.
mean.female <- cbind(
  mean(na.omit(all$woman)),
  mean(na.omit(dems$woman)),
  mean(na.omit(reps$woman)),
  mean(na.omit(women$woman)),
  mean(na.omit(men$woman))
)

mean.rep <- cbind(
  mean(na.omit(all$republican)),
  mean(na.omit(dems$republican)),
  mean(na.omit(reps$republican)),
  mean(na.omit(women$republican)),
  mean(na.omit(men$republican))
)

mean.white <- cbind(
  mean(na.omit(all$race == 1)),
  mean(na.omit(dems$race == 1)),
  mean(na.omit(reps$race == 1)),
  mean(na.omit(women$race == 1)),
  mean(na.omit(men$race == 1))
)

mean.yearb <- cbind(
  mean(na.omit(all$yearb)),
  mean(na.omit(dems$yearb)),
  mean(na.omit(reps$yearb)),
  mean(na.omit(women$yearb)),
  mean(na.omit(men$yearb))
)

no_judges <- cbind(
  nrow(all), nrow(dems),
  nrow(reps), nrow(women), nrow(men)
)

# Combine all of the above information
# into one table.
demographic_table <- rbind(
  mean.kids, mean.girls, prop.zero, prop.one,
  prop.two, prop.three, prop.four, prop.five, prop.six.or.greater,
  mean.female, mean.rep, mean.white, mean.yearb, no_judges
)

# Add descriptive column names to the table.
colnames(demographic_table) <- c(
  "All", "Democrats",
  "Republicans", "Women", "Men"
)

# Add descriptive row names to the table.
rownames(demographic_table) <- c(
  "Mean No. Children",
  "Mean No. Girls",
  "Proportion who have 0 children", "1 children",
  "2 children", "3 children",
  "4 children", "5 Children", "6 Children or More",
  "Proportion Female", "Proportion Republican",
  "Proportion White", "Mean Year Born", "N"
)

# Use kable to output the table.
# Round the decimals to two places.
# Use full width to set chart to full
# width on the page.
kable(demographic_table, digits = 2, caption = "Table 2: Demographics 
      of U.S. Courts of Appeals Judges Who Voted on 
      Gender-Related Cases, 1996-2002") %>%
  kable_styling(full_width = F)
```

Table 2 looks great, really nice titles on the tables

```{r calculate, echo = FALSE, display = FALSE, include = FALSE}

########################################################
## Calculating the Weights (Number of Cases)
########################################################

# Add a new column to the "judge.means" dataframe
# that has the number of cases each judge has decided.
# This will be used as weights for each judge in later
# regressions, because we don't want judges who have
# decided more cases to skew our results (i.e., have
# their decisions matter more).
no_cases <- matrix(data = NA, nrow = nrow(judge.means), ncol = 1)
for (i in 1:length(no_cases)) {
  no_cases[i] <- nrow(women.cases[which(women.cases$name == judge.means$name[i]), ])
}

judge.means <- cbind(judge.means, no_cases)

# Confirm total number of cases. Should be 2,674
# as reported in the paper.
sum(judge.means$no_cases)

########################################################
## Calculating the Outcome Var
########################################################

# Add a new column that calculates the
# number of "liberal" (i.e., "feminist")
# decisions that each judge has made.
no_liberalvote <- matrix(data = NA, nrow = nrow(judge.means), ncol = 1)
for (i in 1:length(no_liberalvote)) {
  stuff <- women.cases[which(women.cases$name == judge.means$name[i]), ]
  no_liberalvote[i] <- nrow(subset(stuff, vote == 2 | vote == 3))
}

lib_vote_share <- no_liberalvote / no_cases

# Add it to the judge.means dataframe,
# and ignore judges (again, for some reason)
# that have no child information.
judge.means <- cbind(judge.means, no_liberalvote, lib_vote_share)
judge.means <- subset(judge.means, girls != "NaN")

########################################################
## Subsetting Data to Various Populations (for use later)
########################################################

# Separate out subsets of the entire judge
# group that fall into four groups: women,
# men, Republican, and Democrat.
women.means <- subset(judge.means, woman == 1)
men.means <- subset(judge.means, woman == 0)
rep.means <- subset(judge.means, republican == 1)
dem.means <- subset(judge.means, republican == 0)
```

Excellent comments above detailing what the authors are doing. This is very useful for me and you.

```{r echo = FALSE, fig.align="center"}
########################################################
## Figure 1
########################################################

# Plot the proportion of cases decided in a 
# "feminist" direction for Republican and Democrat
# judges (and both together). Dem is coded blue
# and Rep as red.
ggplot(judge.means, aes(lib_vote_share)) +
  geom_density() +
  geom_density(
    data = rep.means,
    aes(lib_vote_share, color = "blue"),
    linetype = "dashed"
  ) +
  geom_density(
    data = dem.means,
    aes(lib_vote_share, color = "red"),
    linetype = "dotted"
  ) +
  geom_vline(xintercept = .5, linetype = 2, alpha = .25) +
  xlim(-.4, 1.4) + ylim(0, 2.5) +
  labs(
    x = "Proportion of Cases Decided in a Feminist Direction",
    title = "Figure 1: Distribution of the Proportion of CasesDecided in a Feminist Direction \n out of All Gender-Related Cases Decided, 1996-2002"
  ) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "none"
  ) +
  annotate("text", label = "Less Feminist", x = .3, y = 2.5, color = "grey", size = 4) +
  annotate("text", label = "More Feminist", x = .7, y = 2.5, color = "grey", size = 4) +
  annotate("text", label = "Republicans", x = 0, y = 1.25, color = "red", size = 4) +
  annotate("text", label = "Democrats", x = .9, y = .85, color = "blue", size = 4) +
  annotate("text", label = "All", x = .2, y = .75, size = 4) +
  geom_rect(xmin = -.5, xmax = 0, ymin = 0, ymax = .75, color = "white", fill = "white") +
  geom_rect(xmin = 1, xmax = 1.5, ymin = 0, ymax = .75, color = "white", fill = "white")
```
Nice looking plot, probably better than what is actually in the paper!

```{r, echo = FALSE}
#########
# Table 3
#########

# This shows the distribution of
# number of gender-related cases
# heard per judge in the three 
# groups (all, Reps, and Dems).
gg <- rbind(
  summary(judge.means$no_cases),
  summary(dem.means$no_cases),
  summary(rep.means$no_cases)
)

# Add row names and print
# the table.
rownames(gg) <- c("All Judges", "Democrats", "Republicans")

kable(gg,
  caption = "Table 3: Distribution of the number 
      of gender-related cases heard per judge, 1996-2002.",
  digits = 2
) %>%
  kable_styling(full_width = F)
```

Good

```{r table4, echo = FALSE}
########################################################
## Table 4: Core Results (WLS) Calculations
########################################################

################ Results for all judges
# judge.means <- subset(judge.means, child > 0)

# Regress liberal vote share on
# number of girls. Include child FE
# (i.e., only look for trends within
# groups of judges with the same number of
# total children) and weight by number of
# total cases decided.
my.out1 <- lm(lib_vote_share ~ as.factor(girls) + as.factor(child),
  data = judge.means, weights = judge.means$no_cases
)

# Regress liberal vote share on
# having a girl at all. Child FE and
# case number weights.
my.out2 <- lm(lib_vote_share ~ I(girls > 0) + as.factor(child),
  data = judge.means, weights = judge.means$no_cases
)

# Regress liberal vote share on
# having a girl at all while controlling
# for being Republican, age, Catholic,
# a woman, AfAm or Hispanic. Child FE and
# case number weights.
my.out3 <- lm(lib_vote_share ~ I(girls > 0) + as.factor(child) +
  republican + age + I(religion == 4) + woman +
  I(race == 2) + I(race == 3),
data = judge.means, weights = judge.means$no_cases
)

# Same regression as my.out3 but controlling
# for circuit number.
my.out4 <- lm(lib_vote_share ~ I(girls > 0) + as.factor(child) +
  republican + age + I(religion == 4) + woman +
  I(race == 2) + I(race == 3) + as.factor(circuit.1),
data = judge.means, weights = judge.means$no_cases
)

################ Results for judges with between 1 and 4 children.

# Regress liberal vote share
# on number of girls for a subset
# of the judges.
my.out5 <- lm(lib_vote_share ~ as.factor(girls) + as.factor(child),
  data = subset(judge.means, child < 5 & child > 0), weights = judge.means$no_cases[which(judge.means$child > 0 & judge.means$child < 5)]
)

# Regress vote share on having one girl.
my.out6 <- lm(lib_vote_share ~ I(girls > 0) + as.factor(child),
  data = subset(judge.means, child < 5 & child > 0), weights = judge.means$no_cases[which(judge.means$child > 0 & judge.means$child < 5)]
)

# Regress vote share on having
# one girl, plus six control variables.
my.out7 <- lm(lib_vote_share ~ I(girls > 0) + as.factor(child) + republican +
  age + I(religion == 4) + woman + I(race == 2) + I(race == 3),
data = subset(judge.means, child < 5 & child > 0), weights = judge.means$no_cases[which(judge.means$child > 0 & judge.means$child < 5)]
)

# Regress vote share on having one girl,
# plus seven control variables (including
# circuit).
my.out8 <- lm(lib_vote_share ~ I(girls > 0) + as.factor(child) + republican +
  age + I(religion == 4) + woman + I(race == 2) + I(race == 3) +
  as.factor(circuit.1),
data = subset(judge.means, child < 5 & child > 0), weights = judge.means$no_cases[which(judge.means$child > 0 & judge.means$child < 5)]
)
```

***

```{r t4, results='asis', echo = FALSE}
########################################################
## Table 4: Core Results (WLS) Tables
########################################################

stargazer(my.out1, my.out2, my.out3, my.out4, my.out5, my.out6, my.out7, my.out8,
  header = FALSE,
  style = "ajps",
  type = "html",
  omit.stat = c("f", "ser"),
  dep.var.labels = "Table 4: Weighted Least Squares Results, Gender-Related Cases Only",
  notes = "Outcome is proportion of feminist votes.  Models 1--4 are for all judges, while Models 5--8 are for judges with 1--4 children.  (No judge among those with 1--4 children had four girls.) All models include fixed effects for number of children and use weights based on the number of cases heard by each judge.",
  digits = 2,
  omit = c("circuit"),
  covariate.labels = c("1 Girl", "2 Girls", "3 Girls", "4 Girls", "5 Girls", "At Least 1 Girl", "1 Child", "2 Children", "3 Children", "4 Children", "5 Children", "6 Children", "7 Children", "8 Children", "9 Children", "Republican", "Age at Investiture", "Catholic", "Woman", "African American", "Hispanic", "Constant")
)
```
Beautiful regression table, but make sure the footnotes of the table explaining what indicates signigicance mirrors what is actually in the table

```{r table5, echo = FALSE, include = FALSE, display = FALSE}

#######################################################
## Table 5: Core Results (Case-Level)
#######################################################

# Logit regression of liberal vote share on number of girls (up to 3).
# With child FE (as with all later ones in this section).
my.out7 <- glm(progressive.vote ~ as.factor(girls) + as.factor(child),
               family = binomial(link = "logit"),
               data = subset(women.cases, child < 5 & child > 0))

# Logit regression of liberal vote share on having at least one girl.
my.out8 <- glm(progressive.vote ~ I(girls > 0) + as.factor(child),
               family = binomial("logit"),
               data = subset(women.cases, child < 5 & child > 0))

# Logit regression of vote share on having at least 
# one girl, controlling for Republican, age, Catholic,
# woman, AfAm, and Hispanic. Also year FE and circuit FE (as
# with all later regressions in this section).
my.out9 <- glm(progressive.vote ~ I(girls > 0) + as.factor(child) + republican + age +
                 I(religion == 4) + woman + I(race == 2) + I(race == 3) + as.factor(circuit) +
                 as.factor(year),
               family = binomial("logit"),
               data = subset(women.cases, child < 5 & child > 0))

# Logit regression like the one above, 
# but including employment, pregnancy, reproduction,
# and Title IX controls.
my.out10 <- glm(progressive.vote ~ I(girls > 0) + as.factor(child) + republican
                + age + I(religion == 4) + woman + I(race == 2) + I(race == 3) + as.factor(circuit) + as.factor(year) + as.factor(area),
               family = binomial("logit"),
               data = subset(women.cases, child < 5 & child > 0))

# Final logit regression should
# have case-level clustered SEs, but this one does not.
my.out11 <- glm(progressive.vote ~ I(girls > 0) + as.factor(child) + republican
  + age + I(religion == 4) + woman + I(race == 2) + I(race == 3) + as.factor(circuit) + as.factor(year)
  + as.factor(area),
  family = binomial("logit"),
               data = subset(women.cases, child < 5 & child > 0))

# Below should include clustered
# standard errors, but this version
# does not.

# my.out12 <- glm(progressive.vote ~ I(girls > 0) + as.factor(child) + republican
#   + age + I(religion == 4) + woman + I(race == 2) + I(race == 3) + as.factor(circuit) + as.factor(year)
#   + as.factor(area),
#   data = subset(women.cases, child < 5 & child > 0),
#   family = binomial("logit"))

## Note: Running the ordered logit with polr, in subsetting the data, there are some case areas
## in which there are no observations. Those coefficients are being dropped at POLR gives an
## warning. Nothing to worry.

## Now: Calculating standard errors bootstrapped at the case level:
## Note: This takes about 10 minutes to run.

## Grab the data for these two models
# mod12 <- as.formula("~ progressive.vote + vote + girls +  child + republican +race + age + religion + woman + circuit + year + area + casename")
# dat12 <- model.frame(mod12, data = subset(women.cases, child < 5 & child > 0))
# dat12$casename <- as.character(dat12$casename)

## Create list of data.frames for each case for easy reference
# casenames <- sort(unique(dat12$casename))
# caselist <- lapply(casenames, function(x) dat12[which(dat12$casename == x), ])
# names(caselist) <- casenames

## Running the bootstraps
## Note that not all of the coefficients will be sampled in any given of the
## bootstraps - this might result in some warnings form polr
## (the ordered logit), but is not a problem for the results

# boots <- 1000
# b.star11 <- matrix(NA, ncol =length(my.out11$result$coef), nrow = boots)
# colnames(b.star11) <- names(my.out11$result$coef)
# b.star12 <- matrix(NA, ncol =length(my.out12$result$coef), nrow = boots)
# colnames(b.star12) <- names(my.out12$result$coef)
# set.seed(1234)
# for (b in 1:boots) {
# 	if ((b%%10) == 0) cat("boot: ", b, "\n")
# 	clust.sample <- sample(casenames, replace = TRUE)
# 	c.boot <- do.call(rbind,lapply(clust.sample,function(x) caselist[[x]]))
# 	out11.star <- glm(progressive.vote ~ I(girls>0) + as.factor(child) + republican
# 	+ age + I(religion == 4) + woman + I(race == 2) + I(race == 3) + as.factor(circuit) + as.factor(year) + as.factor(area), data = c.boot, family = binomial("logit"))
#    out12.star <- polr(as.factor(vote) ~ I(girls>0) + as.factor(child) + republican + age + I(religion == 4) + woman + I(race == 2) + I(race ==3) + as.factor(circuit) + as.factor(year) + as.factor(area), data = c.boot)
#  b.star11[b,names(out11.star$coef)] <- out11.star$coef
# 	b.star12[b,names(out12.star$coef)] <- out12.star$coef
# 		}
# bcse11 <- apply(b.star11, 2, sd, na.rm=TRUE)
# bcse12 <- apply(b.star12, 2, sd, na.rm=TRUE)
# save(list=c("bcse11", "bcse12"), file = "bootstraps.RData")
## End bootstrap code here

## can re-load bootstraped data to avoid having to run previous code
## load("bootstraps.RData")
```

***

```{r t5, results='asis', echo = FALSE, warning = FALSE}

#######################################################
## Table 5: Core Results (Case-Level) Table
#######################################################

stargazer(my.out7, my.out8, my.out9, my.out10, my.out11,
	style = "ajps",
	type = "html",
	omit.stat = c("f","ser"),
	omit = c("circuit", "year", "area"),
	dep.var.labels = "Table 5: Logit and Ordered Logit Results, Gender-Related Cases Only.",
	notes = "Outcome is whether judge in a case votes in a feminist direction (Columns 1--5) or in a conservative, moderate, or liberal direction (Column 6).  All models include fixed effects for total number of children and Columns 3--6 include circuit and year fixed effects. Column 5 additionally includes standard errors clustered at the case level",
	covariate.labels = c("1 Girl","2 Girls","3 Girls","At Least 1 Girl",
	"Republican","Age at Investiture","Catholic","Woman",
	"African American","Hispanic", "Employment","Pregnancy","Reproduction","Title IX","Constant"), se = list(my.out7 = NULL, my.out8 = NULL, my.out8 = NULL, my.out10 = NULL,my.out11 = NULL), digits = 2)
```
Another great looking table, as comment as above regarding footnote indicating significance 
***

```{r table7, echo = FALSE, warning = FALSE}

##############################
### Table 7
##############################

# Limit the sample to only judges with 1-4 kids.
rep.means <- filter(rep.means, child < 5 & child > 0)
dem.means <- filter(dem.means, child < 5 & child > 0)
men.means <- filter(men.means, child < 5 & child > 0)
women.means <- filter(women.means, child < 5 & child > 0)

# Do the same for cases.
rep.cases <- filter(women.cases, child < 5 & child > 0 & republican == 1)
dem.cases <- filter(women.cases, child < 5 & child > 0 & republican == 0)
men.cases <- filter(women.cases, woman == 0)
women.cases <- filter(women.cases, woman == 1)

### Party

my.outPARTY <- lm(lib_vote_share ~ I(girls > 0) * republican + as.factor(child),
  data = judge.means, weights = judge.means$no_cases
)

## for republicans

my.outREP <- lm(lib_vote_share ~ I(girls > 0) + as.factor(child),
  data = rep.means, weights = rep.means$no_cases
)


## for democrats

my.outDEM <- lm(lib_vote_share ~ I(girls > 0) + as.factor(child),
  data = dem.means, weights = dem.means$no_cases
)

################ Gender

## for men

my.outGENDER <- lm(lib_vote_share ~ I(girls > 0) * woman + as.factor(child),
  data = judge.means, weights = judge.means$no_cases
)

## for men

my.outMEN <- lm(lib_vote_share ~ I(girls > 0) + as.factor(child),
  data = men.means, weights = men.means$no_cases
)

## for women

my.outWOMEN <- lm(lib_vote_share ~ I(girls > 0) + as.factor(child),
  data = women.means, weights = women.means$no_cases
)

my.outREPMEN <- lm(lib_vote_share ~ I(girls > 0) + as.factor(child),
  data = subset(men.means, republican == 1), weights = men.means$no_cases[which(men.means$republican == 1)]
)
```


```{r t7, results='asis', echo = FALSE, warning = FALSE}

stargazer(my.outREP, my.outDEM, my.outMEN, my.outWOMEN, my.outREPMEN,
  header = FALSE,
  type = "html",
  style = "ajps", omit.stat = c("f", "ser"),
  dep.var.labels = "Table 7: Weighted Least Squares Results",
  digits = 2, covariate.labels = c(
    "At Least 1 Girl",
    "2 Children",
    "3 Children",
    "4 Children",
    "Constant"
  ),
  notes = "Outcome is judges' proportion of feminist votes on gender-related cases. All models include fixed effects for total number of children and use weights based on the number of cases heard by each judge.",
  label = "t:results_party"
)
```

***

```{r TABLE8, echo = FALSE, display = FALSE, include = FALSE}

########################################################
## Table 8: Judges with 0 or 1 child
########################################################

## Including people who have zero children as a control
## suggested by AJPS editor
## (Note: Caution against making inferences on effect of
## daughters among people with 0 children)

my.out12 <- lm(lib_vote_share ~ I(girls > 0) + as.factor(child),
  data = subset(judge.means, child < 2),
  weights = judge.means$no_cases[which(judge.means$child < 2)]
)
summary(my.out12)

my.out13 <- lm(lib_vote_share ~ I(girls > 0),
  data = subset(judge.means, child == 1),
  weights = judge.means$no_cases[which(judge.means$child == 1)]
)
summary(my.out13)

## and then controlling for rep or dem:

my.out14 <- lm(lib_vote_share ~ I(girls > 0) + I(republican == 1),
  data = subset(judge.means, child == 1),
  weights = judge.means$no_cases[which(judge.means$child == 1)]
)
summary(my.out14)
```

```{r table8output, echo = FALSE, results='asis'}

# kable(data.frame()) %>%
#  kable_styling(full_width = F, position = "center")

stargazer(my.out12, my.out13, my.out14,
  style = "ajps",
  type = "html",
  digits = 2,
  omit.stat = c("f", "ser"),
  dep.var.labels = "Table 8: Voting Record in Feminist Direction (Voting Record in Feminist Direction)"
)
```

***

```{r TABLE9,  echo = FALSE, display = FALSE, include = FALSE}

########################################################
## Table 9: Distribution of gender-related cases
########################################################


## just republicans:
rep.means <- subset(judge.means, republican == 1)

## just democrats
dem.means <- subset(judge.means, republican == 0)

aa <- table(dem.means$child, dem.means$girl)
bb <- table(rep.means$child, rep.means$girl)

aa.1 <- prop.table(table(dem.means$child, dem.means$girl), 1)
bb.1 <- prop.table(table(rep.means$child, rep.means$girl), 1)

colnames(aa.1) <- c(
  "0 Girls",
  "1 Girl",
  "2 Girls",
  "3 Girls",
  "4 Girls",
  "5 Girls"
)

colnames(bb.1) <- c(
  "0 Girls",
  "1 Girl",
  "2 Girls",
  "3 Girls",
  "4 Girls"
)
```

```{r table9output, echo = FALSE}

kable(cbind(aa.1, bb.1),
  caption = "Table 9: Proportion of Girls (Conditional on Number of Children) for U.S. Courts of Appeals Judges Participating in Gender-Related Cases, 1996-2002",
  digits = 2
) %>%
  kable_styling(full_width = F)
```
Excellent job, this is a great replication. Really beautiful and well captioned tables, excellent figure, very thorough and clear comments
